Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-24 parallel.tex
putting in draft of unigrid scaling plot + documents.

% Brian to work on this, scaling data from Harkness

>>>>

% Brian to work on this, scaling data from Harkness
Figure~\ref{fig.uniscale} shows \enzo\ weak scaling for a sequence of
scaled non-AMR Lyman alpha forest calculations on NICS Kraken XT4 and
ORNL Jaguar XT4 using decomposition with $128^3$ root grid tiles.  The
grid resolution is of constant physical size.  Scaling up to 98,304
cores has been achieved on the NICS Kraken XT5 using a hybrid-parallel
version of \enzo\.  Excellent scaling in unigrid mode is seen as long
as each core is given enough work -- somewhere around $128^3$
cells/core seems to be about right.

\begin{figure}
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/enzo_unigrid_weak_scaling.eps}
\caption{Unigrid scaling.  ENZO weak scaling performance for a set of
  Lyman Alpha Forest cosmology sim- ulations with constant physical
  resolution per mesh point, showing cell updates per second per
  computational core plotted as a function of the number of root grid
  tiles of dimension $128^3$ (R) in each dimension. The number of MPI
  tasks is N$ = R^3$, so R$ = 16$ on this plot corresponds to a $2048^3$ computational mesh running on 4096 MPI tasks. }
\label{fig.uniscale}
\end{center}
\end{figure}
